An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/learner.tex
update learner slightly

Note that the formalism relies on Algorithm~\ref{alg:plearn}. For brevity, Algorithm 1 only considers
templates without mixed types; that is, the arguments of the template are all of the same type. This is
demonstrated via the filtration step, which filters rules in a file that are possibly of the same type.  
Adding support for mixed types would be handled in a branching statement in Algorithm 1.
Note that in Algorithm~\ref{alg:crules}, constructRule refers to the creation of a rule from a tuple of entries, $u = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
Then the rule creation is formally represented as $t(k(e_1), k(e_2), \ldots, k(e_i), \ldots, k(e_{n-1}))$; in order to 
determine if the rule satisfied, the relation associated with $t(v(e_1), v(e_2), \ldots, v(e_i), \ldots, v(e_{n-1}))$ is evaluated.

@@

With a configuration file that has been verified against catastrophic
failures (\eg, entry missing, type and ordering errors), 
the user may also want to find out more subtle issues.
Anomalous values can cause tricky, but impactful, performance and memory
issues that are hard to debug, as discussed in Example 4 of 
$\S$\ref{sec-motiv}. 
Consequently, anomalous values should be flagged and a warning returned
to the user indicating the violation.

>>>>

Note that the formalism relies on Algorithm~\ref{alg:plearn}. For brevity, Algorithm 1 only considers
templates without mixed types; that is, the arguments of the template are all of the same type. This is
demonstrated via the filtration step, which filters rules in a file that are possibly of the same type.  
Adding support for mixed types would be handled in a branching statement in Algorithm 1.
Note that in Algorithm~\ref{alg:crules}, constructRule refers to the creation of a rule from a tuple of entries, $u = (e_1, e_2, \ldots, e_i, \ldots, e_{n-1})$.
Then the rule creation is formally represented as $t(k(e_1), k(e_2), \ldots, k(e_i), \ldots, k(e_{n-1}))$; in order to 
determine if the rule satisfied, the relation associated with $t(v(e_1), v(e_2), \ldots, v(e_i), \ldots, v(e_{n-1}))$ is evaluated for truth.

@@

With a configuration file that has been verified against catastrophic
failures (\eg, entry missing, type, and ordering errors), 
the user may also want to examine more subtle issues.
Anomalous values can cause tricky, but impactful, performance and memory
issues that are hard to debug, as discussed in Example 4 of 
$\S$\ref{sec-motiv}. 
Consequently, anomalous values should be flagged and a warning returned
to the user indicating the violation.
